### 2013-07-30 paper.tex
k

\section{Problem Statement}
\label{sec:probstate}
\begin{definition}
	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are \emph{orthogonal} if their product is zero.
\end{definition}
Fix an expression $\ul r$.  If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.  More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.  In other words, any two maps with nonzero product can be used to construct an idempotent.

However, if we are interested in finding sets of pairwise orthogonal idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.  The construction of such a set of idempotents is closely related to the decomposition of these bimodules, which in turn gives information about the Soergel bimodules\footnote{Actually, the Soergel bimodules may be defined as the images of idempotents in the endomorphism rings of the Bott-Samelson bimodules.}.

>>>>

\section{Problem Statement}
\label{sec:probstate}
\begin{definition}
	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are \emph{orthogonal} if their product is zero.
\end{definition}
If we can find two half-maps $A$ and $B$ (with the same top and base) for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.  More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.  In other words, any two maps with nonzero product can be used to construct an idempotent.

However, if we are interested in finding sets of \emph{pairwise orthogonal} idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.  The construction of such a set of idempotents is closely related to the decomposition of these bimodules, which in turn gives information about the Soergel bimodules\footnote{Actually, the Soergel bimodules may be defined as the images of idempotents in the endomorphism rings of the Bott-Samelson bimodules.}.
